Quality of Service with Software Defined Network.

### 2017-01-30 report/paper.tex
added openflow messages

\subsection{Openflow 1.0 messages}
Openflow defines a number of messages between a controller and a switch. Now there will be presented some messages we exploited:
\begin{itemize}
	\item[Hello] this message is exchanged between a switch who is looking for a controller after the
	switch was turned on. After receiving it, the controller will send the FeatureReq packet to that switch.
	\item[FeatureReq] this is the message that the controller sends to a switch to know its abilities. The switch
	respond with a FeatureRes and when this last message reaches the pox controller, the ConnectionUp event is raised.
	With the featureRes the controller will know how many ports a switch has and their properties (e.g. if they are connected, link speed,...), the flow table capabilities and the supported statistics.
	\item[PortStatus] this message is sent from a switch to the controller, to notify that some ports has changed their status.
		It's useful to check if a port has someone connected
	\item[StatsReq] The controller will send this message to request the statistics. The payload of the message contains the type of statistic the controller want to know.
		The switch then will answer with the Stats reply, if it supports that type of stat. It will send a Bad_Request message if not.
		\item[PacketIn] This message is sent from the switch to the controller whenever a packet arrives and it doesn't match
		any rule. The controller can decide to ignore that type of message, insert this message in a PacketOut message, or set
		a flow rule for packets like this using a FlowMod.
		\item[PacketOut] This message is sent from the controller to forward a packet, which is the payload of the PacketOut message, to some
		port(s).
		\item[FlowMod] This message set, delete or modify a rule inside a switch. Is the message that allows routing.
\end{itemize}

>>>>

\subsection{Openflow 1.0 messages}
Openflow defines a number of messages between a controller and a switch. Now there will be presented some messages we exploited:
\begin{itemize}
	\item[Hello] This message is sent both from the controller and the switch who is looking for a controller after it
	is turned on. If the switch sent the message, the controller, after receiving it, will send the FeatureReq packet to that switch.
	\item[FeatureReq] this is the message that the controller sends to a switch to know its abilities. The switch
	respond with a FeatureRes and when this last message reaches the pox controller, the ConnectionUp event is raised.
	With the featureRes the controller will know how many ports a switch has and their properties (e.g. if they are connected, link speed,...), the flow table capabilities and the supported statistics.
	\item[PortStatus] this message is sent from a switch to the controller, to notify that some ports has changed their status.
		It's useful to check if a port has someone connected
	\item[StatsReq] The controller will send this message to request the statistics. The payload of the message contains the type of statistic the controller want to know.
		The switch then will answer with the Stats reply, if it supports that type of stat. It will send a Bad_Request message if not.
		\item[PacketIn] This message is sent from the switch to the controller whenever a packet arrives and it doesn't match
		any rule. The controller can decide to ignore that type of message, insert this message in a PacketOut message, or set
		a flow rule for packets like this using a FlowMod.
		\item[PacketOut] This message is sent from the controller to forward a packet, which is the payload of the PacketOut message, to some
		port(s).
		\item[FlowMod] This message set, delete or modify a rule inside a switch. Is the message that allows routing.
\end{itemize}
